Finite-time Analysis of Frequentist Strategies for Multi-armed Bandits

### 2018-01-13 Chapter1/feedback.tex
Latest on 13/1/2017

    To illustrate the different types of feedback we will take help of the following example. Let a learner be given a set of finite actions $i\in\A$ such that $|\A|=K$. Let, the environment be such that each action has a probability distribution $D_i$ attached to it which is fixed throughout the time horizon $T$. The learning proceeds as follows, at every timestep the learner selects $m\in\A$ actions and observes some form of feedback vector $R^{obs}_{t}$ (which will be characterized later). Before the learner selects the set of arms the environment draws the feedback vector $F^{env}_t\in[0,1]^{K}$ of $K$ i.i.d random rewards for all actions $i\in\A$ from $D_i,\forall i\in\A$ which it decides to reveal in particular format depending on the form of feedback chosen for the game, that is full information, partial information or bandit feedback. This game is shown in algorithm \ref{alg:OSeqGame}.

\begin{algorithm}[!th]
\caption{An online sequential game}
\label{alg:OSeqGame}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
\State \For{ each timestep $t=1,2,\ldots, T$}
\State The environment chooses a reward vector $F^{env}_{t}= \left[r_{i,t}\sim^{i.i.d} D_{i},\forall i\in\A\right]$.
\State The learner chooses $m$ actions such that $m < K$ following some policy $\pi$, where $\A$ is the set of arms and $|\A|=K$.
\State The learner observes the reward vector $R^{obs}_{t}\subseteq F^{env}_{t}$.
\State \EndFor
\end{algorithmic}
\end{algorithm}

@@

\subsection{Full information feedback}
In full information feedback, when a learner selects $m$ actions then the environment reveals the rewards of all the actions $i\in \A$. Hence, in this form of feedback  the learner observes $R^{obs}_{t} = F^{env}_{t}=[r_{i,t},\forall i\in\A]$. This has been studied in many forms previously in \citet{takimoto2003path}, \citet{kalai2005efficient} or in online prediction with full information feedback in \citet{cesa2006prediction}.

\subsection{Partial information feedback}
In partial information feedback, when a learner selects $m$ actions then the environment reveals the rewards of only those $m$ actions for $m\in \A$. Hence, in this form of feedback  the learner observes $R^{obs}_{t} = [ r_{m,t},\forall m\in\A ]$. This is also sometimes called the semi-bandit feedback and has been studied in \citet{awerbuch2004adaptive},   \citet{mcmahan2004online} and \citet{gyorgy2007line}.

\subsection{Bandit feedback}
In bandit feedback, when a learner selects $m$ actions then the environment reveals a cumulative reward of those $m$ actions for $m\in \A$. Hence, in this form of feedback  the learner observes $R^{obs}_{t} = \sum_{q=1}^{m} r_{q,t}$. Note, that when $m=1$, then the learner observes the reward of only that action that it has chosen out of $K$ actions. Bandit feedback for single action has been extensively studied in literature with many open problems and we focus on its various interpretations in this thesis.

>>>>

    To illustrate the different types of feedback we will take help of the following example. Let a learner be given a set of finite actions $i\in\A$ such that $|\A|=K$. Let, the environment be such that each action has a probability distribution $D_i$ attached to it which is fixed throughout the time horizon $T$. The learning proceeds as follows, at every timestep the learner selects $m\in\A$ actions and observes some form of feedback vector $G^{obs}_{t}$ (which will be characterized later). Before the learner selects the set of arms the environment draws the feedback vector $F^{env}_t\in[0,1]^{K}$ of $K$ i.i.d random rewards for all actions $i\in\A$ from $D_i,\forall i\in\A$ which it decides to reveal in particular format depending on the form of feedback chosen for the game, that is full information, partial information or bandit feedback. This game is shown in algorithm \ref{alg:OSeqGame}.

\begin{algorithm}[!th]
\caption{An online sequential game}
\label{alg:OSeqGame}
\begin{algorithmic}
\State {\bf Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
\State \For{ each timestep $t=1,2,\ldots, T$}
\State The environment chooses a reward vector $F^{env}_{t}= \left[r_{i,t}\sim^{i.i.d} D_{i},\forall i\in\A\right]$.
\State The learner chooses $m$ actions such that $m < K$ following some policy $\pi$, where $\A$ is the set of arms and $|\A|=K$.
\State The learner observes the reward vector $G^{obs}_{t}\subseteq F^{env}_{t}$.
\State \EndFor
\end{algorithmic}
\end{algorithm}

@@

\subsection{Full Information Feedback}
In full information feedback, when a learner selects $m$ actions then the environment reveals the rewards of all the actions $i\in \A$. Hence, in this form of feedback  the learner observes $G^{obs}_{t} = F^{env}_{t}=[r_{i,t},\forall i\in\A]$. This has been studied in many forms previously in \citet{takimoto2003path}, \citet{kalai2005efficient} or in online prediction with full information feedback in \citet{cesa2006prediction}.

\subsection{Partial Information Feedback}
In partial information feedback, when a learner selects $m$ actions then the environment reveals the rewards of only those $m$ actions for $m\in \A$. Hence, in this form of feedback  the learner observes $G^{obs}_{t} = [ r_{m,t},\forall m\in\A ]$. This is also sometimes called the semi-bandit feedback and has been studied in \citet{awerbuch2004adaptive},   \citet{mcmahan2004online} and \citet{gyorgy2007line}.

\subsection{Bandit Feedback}
In bandit feedback, when a learner selects $m$ actions then the environment reveals a cumulative reward of those $m$ actions for $m\in \A$. Hence, in this form of feedback  the learner observes $G^{obs}_{t} = \sum_{q=1}^{m} r_{q,t}$. Note, that when $m=1$, then the learner observes the reward of only that action that it has chosen out of $K$ actions. Bandit feedback for single action has been extensively studied in literature with many open problems and we focus on its various interpretations in this thesis.

### 2018-01-13 Chapter1/types.tex
Latest on 13/1/2017

\subsection{Types of Bandits based on Environment}

@@

\subsection{Types of Bandits based on goal}

@@

\subsubsection{Cumulative regret minimization}
In cumulative regret minimization the goal of the bandit is to minimize the cumulative regret which is the total loss suffered by the learner throughout the time horizon $T$ for not choosing the optimal arm. Formally, we can define the cumulative regret as,

@@

\subsubsection{Simple regret minimization}
In simple regret minimization the goal of the bandit is to minimize the instantaneous regret that is suffered at any  timestep by the learner. Formally, the simple regret at $t$-th timestep where $J_n\in\A$ is the recommendation by the learner at timestep $t$ is defined,

>>>>

\subsection{Types of Bandits Based on Environment}

@@

\subsection{Types of Bandits Based on Goal}

@@

\subsubsection{Cumulative Regret Minimization}
In cumulative regret minimization the goal of the bandit is to minimize the cumulative regret which is the total loss suffered by the learner throughout the time horizon $T$ for not choosing the optimal arm. Formally, we can define the cumulative regret as,

@@

\subsubsection{Simple Regret Minimization}
In simple regret minimization the goal of the bandit is to minimize the instantaneous regret that is suffered at any  timestep by the learner. Formally, the simple regret at $t$-th timestep where $J_n\in\A$ is the recommendation by the learner at timestep $t$ is defined,

### 2018-01-13 Chapter2/related.tex
Latest on 13/1/2017

\subsection{Lower bound in SMAB}

@@

\subsection{The Upper Confidence Bound approach}

@@

\begin{algorithm}[!th]
\caption{UCB1}
\label{alg:ucb1}
\begin{algorithmic}[1]
\State \textbf{Input:} $K$ number of arms with unknown parameters of reward distribution
\State Pull each arm once
 \For{$t=K+1,..., T$}
\State Pull the arm such that $\argmax_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{2\log (t)}{n_i}}\bigg\rbrace$
\State $t:=t+1 $
 \EndFor
\end{algorithmic}
\end{algorithm}

    The intuition behind this algorithm is simple and it follows from the ideas of concentration inequalities in probability measure theory. The term $\sqrt{\dfrac{2\log (t)}{n_i}}$ is called the confidence interval of the arm $i$ and it signifies a measure of uncertainty over the arm $i$ based on the history of observed rewards for that arm. Therefore, lesser the confidence interval, higher is our confidence that the estimated mean $\hat{r}_i$ is lying close to the expected mean $r_i$ of the arm $i$. Also, note that the confidence interval decreases at the rate of $O\left( \dfrac{1}{\sqrt{n_i}}\right)$ which signifies the rate of convergence of $\hat{r}_i$ to $r_i$ and depends on the number of time the arm has been pulled.

@@

    The UCB-Improved  stated in algorithm \ref{alg:ucbi}, proposed in \citet{auer2010ucb}, is a round-based variant of UCB1. An algorithm is \textit{round-based} if it pulls all the arms equal number of times in each round and then eliminates one or more arms that it deems to be sub-optimal. Note, that in this algorithm the confidence interval term is $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ which is constant in the $m$-th round as $n_m$ is fixed for that round and all arms are being pulled an equal number of times in each round. This is unlike UCB1 algorithm where the confidence interval term depends on $n_i$ which is a random variable. Also, note that in UCB-Improved the knowledge of horizon is required before-hand to calculate the confidence intervals whereas no such input is required for UCB1. An illustrative flowchart depicting the main steps is given in Figure \ref{fig:ucbimp}.

@@

\begin{algorithm}[!th]
\caption{MOSS}
\label{alg:moss}
\begin{algorithmic}[1]
\State \textbf{Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
\State Pull each arm once
 \For{$t=K+1,..., T$}
\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K n_i})\rbrace}{n_i}}\bigg\rbrace$
\State $t:=t+1 $
 \EndFor
\end{algorithmic}
\end{algorithm}

    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm (see algorithm \ref{alg:moss}) and showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$. However, the gap-dependent regret of MOSS is $O\left( \frac{K^{2}\log\left(T\Delta^{2}/K\right)}{\Delta}\right)$ and in certain regimes, this can be worse than even UCB1 (see \citet{audibert2009minimax,lattimore2015optimally}).

@@

\begin{algorithm}[!th]
\caption{OCUCB}
\label{alg:ocucb}
\begin{algorithmic}[1]
\State \textbf{Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution, exploration parameter $\alpha$ and $\psi$
\State Pull each arm once
 \For{$t=K+1,..., T$}
\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\alpha\log(\psi\frac{T}{t})}{n_i}}\bigg\rbrace$
\State $t:=t+1 $
 \EndFor
\end{algorithmic}
\end{algorithm}

Recently in \citet{lattimore2015optimally}, the authors showed that the algorithm Optimally Confident UCB (OCUCB) (see algorithm \ref{alg:ocucb}) achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$. This is the best known gap-dependent and gap-independent regret bounds in the stochastic MAB framework. However, unlike our proposed EUCBV algorithm (in chapter \ref{chap:EUCBV}), OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.

\subsubsection{UCB-Variance algorithm}

@@

    Another notable design principle which has recently gained a lot of popularity is the Thompson Sampling (TS) algorithm (\citep{thompson1933likelihood}, \citep{agrawal2011analysis})  and  Bayes-UCB (BU) algorithm \citep{kaufmann2012bayesian}. This TS is stated in algorithm \ref{alg:ts}. The TS algorithm maintains a posterior reward distribution for each arm; at each round, the algorithm samples values from these distributions and the arm corresponding to the highest sample value is chosen. Although TS is found to perform extremely well when the reward distributions are Bernoulli, it is established that with Gaussian priors the worst-case regret can be as bad as $\Omega \left( \sqrt{KT\log T}\right)$ \citep{lattimore2015optimally}. The BU algorithm is an extension of the TS algorithm that takes quartile deviations into consideration while choosing arms.

\subsection{Information Theoretic approach}

@@

\subsection{Discussion on the various confidence intervals}

@@

\begin{table}[!ht]
\caption{Confidence interval of different algorithms}
\label{tab:conf-comp}
\begin{center}
\begin{tabular}{|p{5em}|p{10em}|p{4em}|p{12em}|}
\hline
Algorithm  &  Confidence interval & Horizon as input & Remarks \\
\hline
\hline
UCB1        & $\sqrt{\dfrac{2\log (t)}{n_i}}$ & No & Loose confidence interval leading to high regret upper bounds.\\%\midrule
\hline
\hline
UCBV        & $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{2}$ & No & Confidence interval uses variance estimation.\\
\hline
\hline
UCB-Imp 		& $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ & Yes & Same confidence interval for all arms in a particular round.\\%\midrule
\hline
\hline
MOSS	     	& $\sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K n_i})\rbrace}{n_i}}$ & Yes & Confidence interval is based on dividing the horizon uniformly for $K$ arms.\\%\midrule
\hline
\hline
OCUCB     	& $\sqrt{\dfrac{2\log(\frac{2T}{t})}{n_i}}$ & Yes & Tightest confidence interval with exploration parameter $\alpha=2$, $\psi=2$ leading to order-optimal regret bounds.\\\midrule
\end{tabular}
\end{center}
%\vspace*{-2em}
\end{table}

>>>>

\subsection{Lower Bound in SMAB}

@@

\subsection{The Upper Confidence Bound Approach}

@@

\begin{algorithm}[!th]
\caption{UCB1}
\label{alg:ucb1}
\begin{algorithmic}[1]
\State \textbf{Input:} $K$ number of arms with unknown parameters of reward distribution
\State Pull each arm once
 \For{$t=K+1,..., T$}
\State Pull the arm such that $\argmax_{i\in A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{2\log (t)}{z_i}}\bigg\rbrace$
\State $t:=t+1 $
 \EndFor
\end{algorithmic}
\end{algorithm}

    The intuition behind this algorithm is simple and it follows from the ideas of concentration inequalities in probability measure theory. The term $\sqrt{\dfrac{2\log (t)}{z_i}}$ is called the confidence interval of the arm $i$ and it signifies a measure of uncertainty over the arm $i$ based on the history of observed rewards for that arm. Therefore, lesser the confidence interval, higher is our confidence that the estimated mean $\hat{r}_i$ is lying close to the expected mean $r_i$ of the arm $i$. Also, note that the confidence interval decreases at the rate of $O\left( \dfrac{1}{\sqrt{z_i}}\right)$ which signifies the rate of convergence of $\hat{r}_i$ to $r_i$ and depends on the number of time the arm has been pulled.

@@

    The UCB-Improved  stated in algorithm \ref{alg:ucbi}, proposed in \citet{auer2010ucb}, is a round-based variant of UCB1. An algorithm is \textit{round-based} if it pulls all the arms equal number of times in each round and then eliminates one or more arms that it deems to be sub-optimal. Note, that in this algorithm the confidence interval term is $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ which is constant in the $m$-th round as $n_m$ is fixed for that round and all arms are being pulled an equal number of times in each round. This is unlike UCB1 algorithm where the confidence interval term depends on $z_i$ which is a random variable. Also, note that in UCB-Improved the knowledge of horizon is required before-hand to calculate the confidence intervals whereas no such input is required for UCB1. An illustrative flowchart depicting the main steps is given in Figure \ref{fig:ucbimp}.

@@

\begin{algorithm}[!th]
\caption{MOSS}
\label{alg:moss}
\begin{algorithmic}[1]
\State \textbf{Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution
\State Pull each arm once
 \For{$t=K+1,..., T$}
\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K z_i})\rbrace}{z_i}}\bigg\rbrace$
\State $t:=t+1 $
 \EndFor
\end{algorithmic}
\end{algorithm}

    In the later work of \citet{audibert2009minimax}, the authors propose the MOSS algorithm which stands for Minimax Optimal Strategy in the Stochastic case (see algorithm \ref{alg:moss}). The confidence interval of MOSS is designed in such a way so as to divide the horizon $T$ proportionally between the number of arms $K$ and the number of pulls $z_i$ that each arm is pulled. As the sub-optimal arms are pulled more number of times their confidence interval decreases, indicating that they have been explored sufficiently, forcing MOSS to explore other arms and quickly converging on the optimal arm. Theoretically, \citet{audibert2009minimax}  showed that the worst case gap-independent regret bound of MOSS is $O\left( \sqrt{KT} \right)$ which improves upon UCB1 by a factor of order $\sqrt{\log T}$. However, the gap-dependent regret of MOSS is $O\left( \frac{K^{2}\log\left(T\Delta^{2}/K\right)}{\Delta}\right)$ and in certain regimes, this can be worse than even UCB1 (see \citet{audibert2009minimax,lattimore2015optimally}).

@@

\begin{algorithm}[!th]
\caption{OCUCB}
\label{alg:ocucb}
\begin{algorithmic}[1]
\State \textbf{Input:} Time horizon $T$, $K$ number of arms with unknown parameters of reward distribution, exploration parameter $\alpha$ and $\psi$
\State Pull each arm once
 \For{$t=K+1,..., T$}
\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{\alpha\log(\psi\frac{T}{t})}{z_i}}\bigg\rbrace$
\State $t:=t+1 $
 \EndFor
\end{algorithmic}
\end{algorithm}

Recently in \citet{lattimore2015optimally}, the authors proposed the Optimally Confident UCB (OCUCB) (see algorithm \ref{alg:ocucb}) which incorporates the increasing timestep $t$ in the confidence interval along with the fixed horizon $T$ and exploration parameters $\psi$ and $\alpha$. The authors showed that the algorithm OCUCB achieves order-optimal gap-dependent regret bound of $O\left(\sum_{i=2}^{K}\frac{\log\left(T/H_i\right)}{\Delta_i}\right)$ where $H_i=\sum_{j=1}^{K}\min\left\lbrace \frac{1}{\Delta_i^2},\frac{1}{\Delta_j^2}\right\rbrace$, and a gap-independent regret bound of $O\left( \sqrt{KT}\right)$. This is the best known gap-dependent and gap-independent regret bounds in the stochastic MAB framework. However, unlike our proposed EUCBV algorithm (in chapter \ref{chap:EUCBV}), OCUCB does not take into account the variance of the arms; as a result, empirically  we find  that our algorithm outperforms OCUCB in all the environments considered.

\subsubsection{UCB-Variance Algorithm}

@@

    Another notable design principle which has recently gained a lot of popularity is the Thompson Sampling (TS) algorithm (\citep{thompson1933likelihood}, \citep{agrawal2011analysis})  and  Bayes-UCB (BU) algorithm \citep{kaufmann2012bayesian}. This TS is stated in algorithm \ref{alg:ts}. The TS algorithm is initialized with a uniform prior and it maintains a posterior reward distribution for each arm; at each round, the algorithm samples values from these distributions and the arm corresponding to the highest sample value is chosen. Although TS is found to perform extremely well when the reward distributions are Bernoulli, it is established that with Gaussian priors the worst-case regret can be as bad as $\Omega \left( \sqrt{KT\log T}\right)$ \citep{lattimore2015optimally}. The BU algorithm is an extension of the TS algorithm that takes quartile deviations into consideration while choosing arms.

\subsection{Information Theoretic Approach}

@@

\subsection{Discussion on The Various Confidence Intervals}

@@

\begin{table}[!ht]
\caption{Confidence interval of different algorithms}
\label{tab:conf-comp}
\begin{center}
\begin{tabular}{|p{5em}|p{10em}|p{4em}|p{12em}|}
\hline
Algorithm  &  Confidence interval & Horizon as input & Remarks \\
\hline
\hline
UCB1        & $\sqrt{\dfrac{2\log (t)}{z_i}}$ & No & Loose confidence interval leading to high regret upper bounds.\\%\midrule
\hline
\hline
UCBV        & $\sqrt{\dfrac{2\hat{v}_i\log (t)}{s_i}} + \dfrac{3\log (t)}{2}$ & No & Confidence interval uses variance estimation.\\
\hline
\hline
UCB-Imp 		& $\sqrt{\dfrac{\log{( T\epsilon_{m}^{2})}}{2 n_{m}}}$ & Yes & Same confidence interval for all arms in a particular round.\\%\midrule
\hline
\hline
MOSS	     	& $\sqrt{\dfrac{\max\lbrace 0,\log(\frac{T}{K z_i})\rbrace}{z_i}}$ & Yes & Confidence interval is based on dividing the horizon proportionally between $K$ arms and $z_i$ pulls for each arm.\\%\midrule
\hline
\hline
OCUCB     	& $\sqrt{\dfrac{2\log(\frac{2T}{t})}{z_i}}$ & Yes & Tightest confidence interval with exploration parameter $\alpha=2$, $\psi=2$ leading to order-optimal regret bounds.\\\midrule
\end{tabular}
\end{center}
%\vspace*{-2em}
\end{table}

### 2018-01-13 Chapter4/prevRes.tex
Latest on 13/1/2017

\subsection{Fixed Budget setting}

@@

This algorithm is quite similar to the UCB1 algorithm discussed in \citet{auer2002finite} (see algorithm \ref{alg:ucb1}). The major difference between the two algorithms is the confidence interval such that for UCB1 it is designed for minimizing the cumulative regret but for UCBE it is designed for minimizing simple regret. An illustrative table comparing the two is provided in table \ref{table:comp-exp}.

\begin{table}
\caption{Confidence interval and exploration parameters of different algorithms}
\label{table:comp-exp}
\begin{center}
\begin{tabular}{|p{5em}|p{6em}|p{8em}|p{12em}|}
\hline
Algorithm  &  Confidence interval & Exploration Parameter$(a)$ & Remarks \\
\hline
\hline
UCB1       & $\sqrt{\dfrac{a}{z_i}}$ & \begin{align*}a = 2\log (t)\end{align*} & $a$ is logarithmic in $t$ to minimize cumulative regret. This achieves a balance between exploration and exploitation. Hence, the cumulative regret grows logarithmically with $t$. \\%\midrule
\hline
\hline
UCBE       & $\sqrt{\dfrac{a}{z_i}}$ & \begin{align*}a = \dfrac{25(T-K)}{36 H_1},\\ \text{ where }H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2}\end{align*} & $a$ is linear in $T$ to minimize simple regret. Here, the main concern is to minimize the probability of error at the end of budget $T$ and conduct as much exploration as possible. Hence, a large $a$ helps to reach exponentially low probability of error.\\\midrule
\end{tabular}
\end{center}
\end{table}

@@

\subsection{Successive Accept Reject Algorithm for best-p arms setting}

@@

\subsection{Fixed Confidence setting}

In this setting, the learning algorithm has to suggest the best arm(s) with a fixed confidence (given as input) with as fewer number of attempts as possible. The single best arm identification has been studied in \citet{even2006action}, while for the combinatorial setup \citet{kalyanakrishnan2012pac} have proposed the LUCB algorithm which, on termination, returns  $m$ arms which are at least $\epsilon$ close to the true top-$m$ arms with probability at least $1-\delta$. For a detailed survey of this setup, we refer the reader to \citet{jamieson2014best}.

>>>>

\subsection{Fixed Budget Setting}

@@

This algorithm is quite similar to the UCB1 algorithm discussed in \citet{auer2002finite} (see algorithm \ref{alg:ucb1}). The major difference between the two algorithms is the confidence interval such that for UCB1 it is designed for minimizing the cumulative regret but for UCBE it is designed for minimizing simple regret. The confidence interval of UCBE is of the order $O\left( T\right)$ instead of $O\left(\log T\right)$ which helps UCBE to conduct sufficient exploration to reach an exponentially low probability of error in suggesting the best arm at the end of budget $T$. Note, that the problem complexity factor $H_1$ needs to be provided as input for the initialization of UCBE.

\subsubsection{UCB-Exploration with Variance Algorithm}

The idea of UCBE can be extended to incorporate the estimation of variance while conducting exploration. This idea was first proposed in \citet{audibert2010best} and later studied in a different context in \citet{gabillon2011multi} for identifying the $p$-best arms in a fixed-budget setting. We present UCB-Exploration-Variance (UCBEV) in Algorithm  \ref{alg:ucbev}. Again, as like UCBE, the choice of the confidence interval scales with $T$ rather than $\log (T)$ so that the probability of error in suggesting the best arm at the end of the budget $T$ is exponentially low. Again, like UCBE, the problem complexity factor $H_{\sigma,1}$ (see \citet{gabillon2011multi}) needs to be provided as input for the initialization of UCBEV and furthermore incorporates variance estimates in the complexity factor to conduct better exploration.

\begin{algorithm}[!ht]
\caption{UCBEV}
\label{alg:ucbev}
\begin{algorithmic}[1]
\State \textbf{Input: } The budget $T$, exploration parameter $a$
\State Pull each arm once
\For{$t=K+1,..., T$}
\State Pull the arm such that $\argmax_{i\in \A}\bigg\lbrace\hat{r}_{i} + \sqrt{\dfrac{a}{z_i}}\bigg\rbrace$, where $a = \dfrac{(T-2K)}{H_{\sigma,1}}$ and $H_{\sigma,1}=\sum_{i=1}^{K}\frac{\sigma_{i}+\sqrt{\sigma_{i}^{2}+(16/3)\Delta_{i}}}{\Delta_{i}^{2}}$.
\State $t:=t+1 $
\EndFor
\end{algorithmic}
\end{algorithm}

\subsubsection{Comparison between UCB1, UCBE, and UCBEV}

An illustrative table comparing the UCB1 for SMAB setting, UCBE, and UCBEV for the pure exploration setting is provided in table \ref{table:comp-exp}.

\begin{table}
\caption{Confidence interval and exploration parameters of different algorithms}
\label{table:comp-exp}
\begin{center}
\begin{tabular}{|p{5em}|p{4em}|p{11em}|p{11em}|}
\hline
Algorithm  &  Confidence interval & Exploration Parameter$(a)$ & Remarks \\
\hline
\hline
UCB1       & $\sqrt{\dfrac{a}{z_i}}$ & \begin{align*}a = 2\log (t)\end{align*} & $a$ is logarithmic in $t$ to minimize cumulative regret. This achieves a balance between exploration and exploitation. Hence, the cumulative regret grows logarithmically with $t$. \\%\midrule
\hline
\hline
UCBE       & $\sqrt{\dfrac{a}{z_i}}$ & {\begin{align*}& a = \dfrac{25(T-K)}{36 H_1},\\& \text{ where }H_1 = \sum_{i=1}^{K}\dfrac{1}{\Delta_i^2} 
\end{align*} }
& $a$ is linear in $T$ to minimize simple regret. Here, the main concern is to minimize the probability of error at the end of budget $T$ and conduct as much exploration as possible. Hence, a large $a$ helps to reach exponentially low probability of error.\\
\hline
\hline
UCBEV      & $\sqrt{\dfrac{a}{z_i}}$ & {\begin{align*} & a = \dfrac{(T-2K)}{H_{\sigma,1}},\\ &\text{ where } \\  & H_{\sigma,1}=\sum_{i=1}^{K}\frac{\sigma_{i}+\sqrt{\sigma_{i}^{2}+(16/3)\Delta_{i}}}{\Delta_{i}^{2}} 
\end{align*}}
& Like UCBE, $a$ is linear in $T$ to minimize simple regret. Also, incorporates variance estimates to conduct better exploration.\\\midrule
\end{tabular}
\end{center}
\end{table}

@@

\subsection{Successive Accept Reject Algorithm for Best-p Arms Setting}

@@

\subsection{Fixed Confidence Setting}

In this setting, the learning algorithm has to suggest the best arm(s) with a fixed confidence (given as input) with a fewer number of attempts as possible. The single best arm identification has been studied in \citet{even2006action}, while for the combinatorial setup \citet{kalyanakrishnan2012pac} have proposed the LUCB algorithm which, on termination, returns  $m$ arms which are at least $\epsilon$ close to the true top-$m$ arms with probability at least $1-\delta$. For a detailed survey of this setup, we refer the reader to \citet{jamieson2014best}.
